---
title: "Introduction to gkwdist"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to gkwdist}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Overview

The **gkwdist** package implements the Generalized Kumaraswamy (GKw) 
distribution and six nested sub-families for modeling bounded continuous 
data on the interval (0,1).

## The GKw Family

The five-parameter Generalized Kumaraswamy distribution has PDF:

$$f(x; \alpha, \beta, a, b, \lambda) = \alpha \beta \lambda a b x^{a-1} (1-x^a)^{b-1} [1-(1-x^a)^b]^{\beta-1} \{1-[1-(1-x^a)^b]^\beta\}^{\lambda-1}$$

## Available Distributions

1. **Beta** (`dbeta_`, `pbeta_`, etc.): $a = b = \lambda = 1$
2. **Kumaraswamy** (`dkw`, `pkw`, etc.): $\beta = \lambda = 1$
3. **Exponentiated-Kumaraswamy** (`dekw`): $a = b = 1$
4. **Kumaraswamy-Kumaraswamy** (`dkkw`): $\lambda = 1$
5. **Beta-Kumaraswamy** (`dbkw`): $b = \lambda = 1$
6. **McDonald** (`dmc`): Full 5-parameter model

## Quick Start

```{r example, eval=FALSE}
library(gkwdist)

# Generate random data from Kumaraswamy distribution
set.seed(123)
x <- rkw(n = 1000, alpha = 2, beta = 3)

# Density
d <- dkw(x, alpha = 2, beta = 3)

# Distribution function
p <- pkw(x, alpha = 2, beta = 3)

# Quantiles
q <- qkw(c(0.25, 0.5, 0.75), alpha = 2, beta = 3)

# Visualization
hist(x, probability = TRUE, main = "Kumaraswamy(2, 3)")
curve(dkw(x, 2, 3), add = TRUE, col = "red", lwd = 2)
```

## References

Kumaraswamy, P. (1980). A generalized probability density function for 
double-bounded random processes. *Journal of Hydrology*, 46(1-2), 79-88.
